EEG2fMRI: Cross-Modal Synthesis for Functional Neuroimaging

### 2021-06-24 article/article.tex
Update

\begin{abstract}
    Functional neuroimaging techniques are essential in advancing research in neuroscience. However, existing techniques require researchers to either compromise on spatial resolution, temporal resolution, cost, or portability. We attempt to model the  mapping between concurrent EEG and fMRI recordings using various machine learning architectures (i.e. MLPs, CNNs, and transformers), in order to combine the complementary qualities of the two modalities. The trained model is then able to reconstruct simultaneous fMRI data solely from EEG data. Although initial results in a within-subject regime are promising, the limited quantity of multi-modal recordings currently available appears to be a major obstacle in generalizing to new subjects.
\end{abstract}

@@

In addition to uni-modal synthesis, investigators have also proposed cross-modal synthesis for augmenting neuroimaging techniques \cite{yi_generative_2019}. This consists of reconstructing data collected through a target modality based on data collected through a distinct source modality, by exploiting the inherent relation between them. In a setting where both source and target modalities are available, this task might have limited utility. However, the value of cross-modal synthesis comes from settings where only one modality is available. In such settings, existing data can be used to approximate data collected through the unavailable modality. Unfortunately, this approach has largely been used for augmenting structural neuroimaging, with limited analogous efforts for functional neuroimaging.

@@

\begin{table}
\begin{center}
        \begin{tabular}{|c | c|} 
            \hline
            Model Architecture & MSE \\
            \hline
            fully-connected network & 9.527e-4 \\ 
            convolutional neural network & 7.087e-4 \\ 
            \textbf{transformer} & \textbf{4.976e-4} \\ 
            \hline
           \end{tabular}
           \caption{Mean squared error of different models in a one-subject-left-out regime}
\end{center}
\end{table}

>>>>

\begin{abstract}
    Functional neuroimaging techniques are essential in advancing research in neuroscience. However, existing techniques require researchers to either compromise on spatial resolution, temporal resolution, cost, or portability. We attempt to model the  mapping between concurrent EEG and fMRI recordings using various machine learning architectures (i.e. fully-connected networks, convolutional neural networks, and transformers), in order to combine the complementary qualities of the two modalities. The trained model is then able to reconstruct simultaneous fMRI data solely from EEG data. Although initial results in a within-subject regime are promising, the limited quantity of multi-modal recordings currently available appears to be a major obstacle in generalizing to new subjects.
\end{abstract}

@@

In addition to uni-modal synthesis, investigators have also proposed cross-modal synthesis for augmenting neuroimaging techniques \cite{yi_generative_2019}. This consists of reconstructing data collected through a target modality based on data collected through a different source modality, by exploiting the inherent relation between them. In a setting where both source and target modalities are available, this task might have limited utility. However, the value of cross-modal synthesis comes from settings where only one modality is available. In such settings, existing data can be used to approximate data collected through the unavailable modality. Unfortunately, this approach has largely been used for augmenting structural neuroimaging, with limited analogous efforts for functional neuroimaging.

@@

\begin{center}
        \begin{tabular}{|c | c|} 
            \hline
            Model Architecture & MSE \\
            \hline
            fully-connected network & 9.527e-4 \\ 
            convolutional neural network & 7.087e-4 \\ 
            \textbf{transformer} & \textbf{4.976e-4} \\ 
            \hline
           \end{tabular}
\end{center}

\begin{center}
    Table 1. Mean squared error of different models in a one-subject-left-out regime
\end{center}
